Contracts for unions and intersections are hard for Nickel

### 2021-05-27 paper.tex
[WIP]Add a paragraph on lazyness

\subsubsection*{Lazyness}
\unsure{Should we talk about lazyness?
this would be a good place to introduce it}

>>>>

\subsection*{Lazyness}
Evaluation strategies relates to the evaluation of the expression bound to
identifiers. Expressions are be bound by assignments (e.g. the \nickel{blah} construct in Nickel), or arguments are bound to
parameters in a function application. We will use Figure~\ref{} as a working
example.

The eager strategy consists in evaluating right away a bound value before
storing it in an identifier. If an identifier is not used, this leads to
unnecessary work: in Figure~\ref{}, the expression \nickel{fibonacci 100} would
be computed although it is never used. The lazy strategy, on the other hand,
only evaluates expression if they are needed. In the lazy model, bound
expressions are stored as in their current unevaluated form, also called a
\emph{thunk}. Thunks are only evaluated at their first usage, and their value is
memoized for future usages.

The eager strategy has been chosen in the vast majority of languages: while
theoretically less efficient, it is simpler to implement and more predictable
for the programmer. Also, lazy evaluation can occur performance overhead and
memory leaks in unexpected ways. While eager evaluation is the default, some
languages however offer a form of lazy evaluation, either as an opt-in option
(e.g. Ocaml and ReScript), or by default for specific primitives types such as
like list (e.g.  Swift and Perl6). The most notable lazy language is Haskell
(and its web avatar PureScript). Although rare in general purpose languages,
lazy evaluation is more widespread in the configuration space: the configuration
languages Dhall, CUE and Jsonnet also implements full lazy evaluation. So are
the Nix language, which inspired Nickel, and Nickel itself.
